---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# powersPackage
 __Note__ This package was created to serve as Homework 09 for STAT547.
 
It's abilities are very novice, and serves as an educational tool.
It contains the following functions: `square()`,`cube()`,`reciprocal()`,`quadrtc()`.

#
Package still in progress. So far you can find the cube, sqaure, or reciprocal of numbers, and the root x of a quadratic problem. Graphic functions for the quadratic function has yet to be added.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("farihakhan/powersPackage")
```

## Load and run

```{r}
library(powersPackage)
```

`square(x, genplot=FALSE)`

`cube(x, genplot=FALSE)`

`reciprocal(x, genplot=FALSE)`

`quadrtc(a,b,c)` 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
x <- negtenvec
reciprocal(x)
```
